Towards Verifying the Bitcoin-S Library

### 2019-06-24 paper/paper.tex
more changes
added comments about semantic

\todo{ramon: completely understand and explain the code}

@@

Finally, everything is green and correctly verified. 
\begin{figure}
	\centering
		\includegraphics[width=\textwidth]{final_verify_output}
	\caption{Output of Stainless verification for addition with 0 of Bitcoin-S-Cores CurrencyUnit}
\end{figure}

@@

\todo{Ramon does this change semantics?}

@@

@@

@@

@@

>>>>

\todo{kai: do you need more explanation?}

@@

Finally, everything is green and correctly verified. 
\begin{figure}
	\centering
		\includegraphics[width=\textwidth]{result_output}
	\caption{Output of Stainless verification for addition with 0 of Bitcoin-S-Cores CurrencyUnit}
\end{figure}

@@

\todo{Kai this does not change the semantic}

@@

\todo{kai this does not change the semantic}

@@

\todo{kai this does not change semantic}

@@

\todo{kai This does not change semantic}

@@

\todo{kai here we do not know if it changes semantic}
